Applied Measure Theory for Probabilistic Modeling

### 2022-05-13 paper/paper.tex
edits

For a parameter $\theta$ and data $x$, suppose we have a \href{https://en.wikipedia.org/wiki/Prior_probability}{\emph{prior}} $p(\theta)$ (momentarily assuming Lebesgue base measure) and \href{https://en.wikipedia.org/wiki/Likelihood_function}{\emph{likelihood}} $p(x | \theta)$. Then Bayes's Law gives the posterior density
\[
p(\theta \mid x) = \frac{p(\theta)\ p(x \mid \theta)}{p(x)}\ .
\]

>>>>

Let us momentarily assume the common case of Lebesgue base measure. For a parameter $\theta$ and data $x$, suppose we have a \href{https://en.wikipedia.org/wiki/Prior_probability}{\emph{prior density}} $p(\theta)$ and \href{https://en.wikipedia.org/wiki/Likelihood_function}{\emph{likelihood}} $p(x | \theta)$. Then Bayes's Law gives the posterior density
\[
p(\theta \mid x) = \frac{p(\theta)\ p(x \mid \theta)}{p(x)}\ .
\]
